BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-03-30 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd
notes

@@

time_geodata_writer <- system.time({ # write out collection as GoogleEarth object
  geodata_writer(data, path = 'data/processed', 
               filename = 'Herbarium_Collections_2023',
               filetype = 'kml')
})

>>>>

time_geodata_writer <- system.time({ # write out collection as GoogleEarth object
  geodata_writer(data, path = 'data/processed', 
               filename = 'Herbarium_Collections',
               filetype = 'kml')
})

@@
